%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	%a4paper, % Uncomment for A4 paper size (default is US letter)
	11pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class

\usepackage{ebgaramond} % Use the EB Garamond font
\usepackage[hidelinks]{hyperref}

%------------------------------------------------

\name{LI Shangxuan} % Your name to appear at the top

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines (\\) you use in the \address commands will be converted to symbols, so each address will appear as a single line.

% \address{A1, 16F, 83--97 Nathan Rd., TST} % Main address

% \address{123 Pleasant Lane \\ City, State 12345} % A secondary address (optional)

\address{(+852) 5482-6196 \\ (+86) 134-1828-5202} % Contact information
\address{22626433@life.hkbu.edu.hk \\ work@mxr612.top} % Contact information

%----------------------------------------------------------------------------------------

\begin{document}


\begin{rSection}{Education}

    \textbf{Hong Kong Baptist University} \hfill 2022 --- Present \\
    Associate of Science\\
    (Concentration Studies: Psychology)\\
    % Minor in Linguistics \smallskip \\
    % Member of Eta Kappa Nu \\
    % Member of Upsilon Pi Epsilon \\
    cGPA: 3.58/4.00

    \textbf{Dongguan Middle School Songshan Lake School} \hfill 2019 --- 2022 \\
    High School Diploma \\
    (Science Course Set)\\
    National College Entrance Examination: 543/750

\end{rSection}

\begin{rSection}{Experience}

    \begin{rSubsection}{Program Manager \& Chief Editor}{2024  --- Present}{Student Project: \href{https://psygscales.com/}{PsychoScales}}{}
        \item Built a free website of empirical psychology scales and explanations.
        \item Provided a platform of statistics for analysis between psychology scales.
        \item Introduced Large Language Models with enhanced Psychology knowledge base.
        \item Future functions: item-level scales analysis and semantic analysis based scale analysis.
        \item Practiced program management skills by coordinating website development, content editing, and large language model training, with project dashboard and timeline, leading the project orderly.
        \item Applicated psychology, statistics, and programming skills.
    \end{rSubsection}

    \begin{rSubsection}{Researcher}{2023 --- Present}{Personal Research Project: Freshman Adjustment in Cross-Cultural Aspect}{}
        \item Focused on culture differences of freshman adjustment.
        \item Developed the literature reading ability and accumulated psychological knowledge.
        \item Applicated psychological experiment skill.
    \end{rSubsection}

    % \begin{rSubsection}{Volunteer}{2023}{Hong Kong Federation of Youth Groups}{}
    %     % \item Healthy Transition II program driven by Hong Kong Federation of Youth Groups
    %     \item Being invited to Anti-Drug Animation Festival.
    %     \item Conveied the message by taking part in the recording and creating animations.
    %     \item Enhanced skills in storytelling, graphic design, and animation.
    %     \item Learnt the use of multimedia in the advocation of crucial social causes.
    %     \item Raised awareness about the detrimental impacts of drug abuse on individuals and society.
    % \end{rSubsection}

    \begin{rSubsection}{Mental Health Gate Keeper}{2022 --- 2023}{Hong Kong Baptist University}{}
        \item Certificated after Mental Health First Aid Training.
        \item Participated in the psychology exhibition of wellness week.
        \item Engaged in meaningful dialogues and discussions centered around mental well-being.
        \item Exposed to the latest research, techniques, and tools in the field of psychology.
    \end{rSubsection}

    % \begin{rSubsection}{Student Suicide Prevention \& Secondary Students' Mental Health Enhancement Professional Training}{2022}{Department of Social Work, Hong Kong Baptist University}{}
    %     \item Understood different kinds of mental health distress
    %     \item Equipped with knowledge  for recognizing early signs of suicide and techniques for risk evaluation
    %     \item Familiered with structured early intervention skills and tools before professional help
    % \end{rSubsection}

    \begin{rSubsection}{Informatics Competition Contestant}{2018 --- 2022}{Olympiad in Informatics Team of Dongguan Middle School Songshan Lake School}{}
        \item Joined School Olympiad in Informatics Team.
        \item Took part in Olympiad in Informatics in school, city, province and Nation.
        \item Won National Olympiad in Informatics in Provinces second prize thrice.
        \item Won China Computer Federation Certificated Software Professional second prize once, third prize twice.
        \item Reached China Computer Federation Programming Ability Level 6.
        \item Acquired theoretical and practical programming skills, especially algorithm and data structure knowledge.
        \item Developed thinking and problem-solving ability,
        % \item Accumulated computer using skills
    \end{rSubsection}

\end{rSection}


\begin{rSection}{Technical Strengths}

    \begin{tabular}{@{} >{\bfseries}l @{\hspace{3ex}} l @{}}
        Programming Languages & SPSS, C++, \LaTeX{}                                         \\
        Computer Skills       & Microsoft Office, Zotero, Git                               \\
        Languages             & English (Fluent), Cantonese (Elementary), Mandarin (Native)
    \end{tabular}

\end{rSection}


\begin{rSection}{Self-evaluation}
    \textbf{Programming skills} \\
    Familiar with basic algorithms and data structures such as Searching, Dynamic Programming, Flow, Hash, Segment tree, Balanced Tree, and more. Enjoy learning new languages and algorithms, especially the latest AI technology.

    \textbf{Research Experience } \\
    Passionate about research, enjoying inventing and discovering new things. Positively applied learned research methods in daily studies and now working on a research project in Psychology.

    \textbf{Academic Performence} \\
    Passionate about the Psychology field, strictly demanding my assignments according to academic standards.
    Want to accumulate more research-related skills for further studies.

    \textbf{Group Work} \\
    Often lead team members, completing research tasks efficiently and rigorously.

    \textbf{Personal Interests}\\
    Literary, Photography
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
