\documentclass[]{article}

\usepackage{indentfirst,setspace}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber]{biblatex}
\addbibresource[glob]{References.bib}
% \setmainfont{Times New Roman}

% \doublespacing{}
\renewcommand{\baselinestretch}{1.125}

\title{LI Shangxuan}
% \shorttitle{}
% \author{}
% \authoraffiliations{}
\date{}

\begin{document}

\maketitle

I am a psychology student in the final year of the associate degree program at the College of International Education, Hong Kong Baptist University, and desire to further study psychology.
I have a wide range of interests covering a wide range of topics. I am keen to explore all things unfamiliar, and this is supported by a few scales, like my higher openness in ``NEO PI-R'', more wisdom traits in ``VIA-IS'', and particularly outstanding scores on Investigate in ``Holland Code''.
This proclivity underpinned a profound aspiration to engage in journeys of discovery, characterized by a deep-seated commitment to immersing myself in the intricacies of our surrounding world.
I am mainly passionate about understanding human behaviour and the underlying psychological mechanisms.
I find immense satisfaction in interacting with diverse groups of people, striving to comprehend their varied perspectives.
This intrinsic curiosity has led me down the path of psychology, and my dedication further underpinned my academic journey following my interest in psychology.
When studying at Hong Kong Baptist University, I delved deep into each subject, striving to assimilate theoretical knowledge while seeking real-world applications.
This is finally reflected in my academic honour of ``President's Honour Roll''.

% \section{Mental Health}

In the classroom, I accumulated extensive and solid psychological theories and gained a comprehensive understanding of psychological knowledge.
I was particularly influenced by positive psychology, which provides an astonishing demonstration of the power of psychology to change and empower people.
Outside the classroom, I participated in various psychology-related activities in Hong Kong.
My involvement in initiatives such as the Mental Health First Aid Course and Mental Health Club underscores my commitment to understanding and enhancing psychological well-being as the mainstream topic of psychology today.
The knowledge of mental heath is also applied in my personal life: once, a friend of mine met some mental problem and rang my phone for help.
I calmly used structured first aid methods to evaluate the situation and provided instruction to her, simultaneously requiring professional service.
She was diagnosed with major depression later and is hospitalized now and I am keeping in touch with her and providing support as a friend.

% \section{Culture}

Personally, I am interested in culture and cross-cultural psychology field.
During my associate studies, I was deeply sensitized that culture, functioning as an intrinsic milieu, profoundly influences our cognitive paradigms and behavioural patterns.
% Therefore, psychology needs to uncover the norm differences of populations and how cultural factors relate to them.
% This realization is rooted in the discernment that the majority of psychological investigations, as underscored in the seminal meta-analysis conducted by \textcite{henrich_weirdest_2010}, are overwhelmingly undertaken by Western scholars, predominantly employing samples drawn from Western, Educated, Industrialized, Rich, and Democratic societies.
It is crucial to ensure the generalizability of insights derived from psychological inquiries across a gamut of culturally divergent contexts and bridging the yawning chasm between different cultures' psychological paradigms.
% In an era characterized by the deepening interconnectivity of our world, the salience of cultural psychology has grown exponentially apparent to me:
% Mutual understanding is paramount in a world characterized by a profusion of cultures, each endowed with distinctive norms, behaviours, and symbols.
My personal experiences have consistently corroborated my conviction about this limitation, prompting pivotal inquiries into the universality of psychological research.
These inquiries have assumed a central position in my academic pursuits, closely intertwining with my extracurricular endeavours.
% \section{Research}
These interests prompted me to undertake a demo study titled ``Cross-cultural Comparative Research of First-year Students' Adaptation'', which has spanned four months and remains a work in progress.
The study focuses on understanding the similarities and differences between cultures and the factors related to this result.
This study considers factors such as adolescent growth, socioeconomic status, and differences between internal and external coping mechanisms.
The aim is to comprehensively understand how cultural backgrounds influence students' adaptation to new environments.
My passion for psychology is not confined to my academic and research interests: It defines who I am and the contributions I aim to make to the world.

% \section{Further}

Although I approached professors for mentorship and found hesitance, it has not deterred me.
I remain steadfast in my goal, investing time in reading three papers weekly and furthering my understanding.
I also actively equipped myself with diverse skill sets, ranging from SPSS for empirical research and \LaTeX\ for essay typesetting to my ability to communicate in English and Cantonese.
All these efforts are directed towards achieving my dream.
I want to contribute significantly to bridging this gap through extensive research, focusing on illuminating the unexplored facets of psychology in different cultures.
My vision post-graduation is to continue contributing to the academic sphere, advancing the field of psychology through relentless research and exploration, and imparting my knowledge to the coming generations.
I aspire not only to further my studies with an undergraduate and postgraduate degree in psychology but also to remain within academia, advancing the field through research and teaching.

% \section{Ending}

For me, the path of psychology is not just a career choice but a vocation. I am confident in my ability to contribute significantly to further research with my zeal for cultural psychology and my commitment to academic rigor.
My experiences, both academic and extracurricular, have shaped my perspective, enabling me to approach challenges with an analytical mindset. This makes me an ideal candidate for a graduate program at your esteemed university.
I am keen on joining your respected institution, not just as a student, but as a scholar who brings unique perspectives and makes a lasting impact.

\end{document}
